---
title: "coursera"
output: html_document
---

Copy and paste the R code from the corresponding R file into the text box at the appropriate point in the peer assessment.
Exploratory Data Analysis - Course Project 2
NOTE: My work and answers to the questions are at the bottom of this document.

Introduction
Fine particulate matter (PM2.5) is an ambient air pollutant for which there is strong evidence that it is harmful to human health. In the United States, the Environmental Protection Agency (EPA) is tasked with setting national ambient air quality standards for fine PM and for tracking the emissions of this pollutant into the atmosphere. Approximatly every 3 years, the EPA releases its database on emissions of PM2.5. This database is known as the National Emissions Inventory (NEI). You can read more information about the NEI at the EPA National Emissions Inventory web site.

For each year and for each type of PM source, the NEI records how many tons of PM2.5 were emitted from that source over the course of the entire year. The data that you will use for this assignment are for 1999, 2002, 2005, and 2008.

Data
The data for this assignment are available from the course web site as a single zip file:
  
  Data for Peer Assessment [29Mb]
The zip file contains two files:
  
  PM2.5 Emissions Data (summarySCC_PM25.rds): This file contains a data frame with all of the PM2.5 emissions data for 1999, 2002, 2005, and 2008. For each year, the table contains number of tons of PM2.5 emitted from a specific type of source for the entire year. Here are the first few rows.

    fips      SCC Pollutant Emissions  type year
4  09001 10100401  PM25-PRI    15.714 POINT 1999
8  09001 10100404  PM25-PRI   234.178 POINT 1999
12 09001 10100501  PM25-PRI     0.128 POINT 1999
16 09001 10200401  PM25-PRI     2.036 POINT 1999
20 09001 10200504  PM25-PRI     0.388 POINT 1999
24 09001 10200602  PM25-PRI     1.490 POINT 1999

fips: A five-digit number (represented as a string) indicating the U.S. county
SCC: The name of the source as indicated by a digit string (see source code classification table)
Pollutant: A string indicating the pollutant
Emissions: Amount of PM2.5 emitted, in tons
type: The type of source (point, non-point, on-road, or non-road)
year: The year of emissions recorded
Source Classification Code Table (Source_Classification_Code.rds): This table provides a mapping from the SCC digit strings int he Emissions table to the actual name of the PM2.5 source. The sources are categorized in a few different ways from more general to more specific and you may choose to explore whatever categories you think are most useful. For example, source “10100101” is known as “Ext Comb /Electric Gen /Anthracite Coal /Pulverized Coal”.

You can read each of the two files using the readRDS() function in R. For example, reading in each file can be done with the following code:

## This first line will likely take a few seconds. Be patient!

#NEI <- readRDS("summarySCC_PM25.rds")
#SCC <- readRDS("Source_Classification_Code.rds")


as long as each of those files is in your current working directory (check by calling dir() and see if those files are in the listing).

Assignment
The overall goal of this assignment is to explore the National Emissions Inventory database and see what it say about fine particulate matter pollution in the United states over the 10-year period 1999–2008. You may use any R package you want to support your analysis.

Making and Submitting Plots
For each plot you should

Construct the plot and save it to a PNG file.
Create a separate R code file (plot1.R, plot2.R, etc.) that constructs the corresponding plot, i.e. code in plot1.R constructs the plot1.png plot. Your code file should include code for reading the data so that the plot can be fully reproduced. You should also include the code that creates the PNG file. Only include the code for a single plot (i.e. plot1.R should only include code for producing plot1.png)
Upload the PNG file on the Assignment submission page
Copy and paste the R code from the corresponding R file into the text box at the appropriate point in the peer assessment.
In preparation we first ensure the data sets archive is downloaded and extracted.


```{r}
archiveFile <- "NEI_data.zip"
if(!file.exists(archiveFile)) {
  archiveURL <- "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip"
  if(Sys.info()["sysname"] == "Darwin") {
    download.file(url=archiveURL,destfile=archiveFile,method="curl")
  } else {
    download.file(url=url,destfile=archiveFile)
  }
}
if(!(file.exists("summarySCC_PM25.rds") && 
     file.exists("Source_Classification_Code.rds"))) { unzip(archiveFile) }

NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
```

```{r}
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
```

Questions
You must address the following questions and tasks in your exploratory analysis. For each question/task you will need to make a single plot. Unless specified, you can use any plotting system in R to make your plot.

Question 1
First we'll aggregate the total PM2.5 emission from all sources for each of the years 1999, 2002, 2005, and 2008.

```{r}
aggTotals <- aggregate(Emissions ~ year,NEI, sum)

barplot(
  (aggTotals$Emissions)/10^6,
  names.arg=aggTotals$year,
  xlab="Years",
  ylab="PM2.5 Emissions (10^6 Tons)",
  main="Total PM2.5 Emissions From All US Sources"
)
```

Have total emissions from PM2.5 decreased in the United States from 1999 to 2008?

it has a total emissions have decreased in the US from 1999 to 2008, on 1999 had too high emissions.


Question 2
First we aggregate total emissions from PM2.5 for Baltimore City, Maryland (fips="24510") from 1999 to 2008.

```{r}
baltNEI <- NEI[NEI$fips=="24510",]
aggTotalsBaltimore <- aggregate(Emissions ~ year, baltNEI,sum)

barplot(
  aggTotalsBaltimore$Emissions,
  names.arg=aggTotalsBaltimore$year,
  xlab="Years",
  ylab="PM2.5 Emissions",
  main="Graphic Total PM2.5 Emissions From All Baltimore City Sources"
)
```

Have total emissions from PM2.5 decreased in the Baltimore City, Maryland (fips == "24510") from 1999 to 2008?

From the graphics said than have decreased in Baltimore City  on  2008 and its the best years from all.

Question 3
Using the ggplot2 plotting system,

```{r}
library(ggplot2)

ggp <- ggplot(baltNEI,aes(factor(year),Emissions,fill=type)) +
  geom_bar(stat="identity") +
  theme_bw() + guides(fill=FALSE)+
  facet_grid(.~type,scales = "free",space="free") + 
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (Tons)")) + 
  labs(title=expression("PM"[2.5]*" Emissions, Baltimore City 1999-2008"))

print(ggp)

```

Of the four types of sources indicated by the type (point, nonpoint, onroad, nonroad) variable, which of these four sources have seen decreases in emissions from 1999–2008 for Baltimore City?

it used all almost (non-road, nonpoint, on-road) have all seen decreased emissions overall in Baltimore City.

Which have seen increases in emissions from 1999–2008?

the worst it was nonpoint and the slowest was onroad. We can said all points have decreased until 2005 and this years up.


Question 4
First we subset coal combustion source factors NEI data.

```{r}
Combustion_Related <- grepl("comb", SCC$SCC.Level.One, ignore.case=TRUE)
CoalRelated <- grepl("coal", SCC$SCC.Level.Four, ignore.case=TRUE) 
CoalCombustion <- (Combustion_Related & CoalRelated)
CombustionSCC <- SCC[CoalCombustion,]$SCC
CombustionNEI <- NEI[NEI$SCC %in% CombustionSCC,]

library(ggplot2)

ggp <- ggplot(CombustionNEI,aes(factor(year),Emissions/10^5)) +
  geom_bar(stat="identity",fill="grey",width=0.75) +
  theme_bw() +  guides(fill=FALSE) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (10^5 Tons)")) + 
  labs(title=expression("PM"[2.5]*" Coal Combustion Source Emissions Across US from 1999-2008"))

print(ggp)
```

Across the United States, how have emissions from coal combustion-related sources changed from 1999–2008?

Emissions from coal combustion related sources have decreased from 1999-2008 and the 2008 is the best year from all on this studio.


Question 5
First we subset the motor vehicles, which we assume is anything like Motor Vehicle in SCC.Level.Two.

```{r}
Vehicles <- grepl("vehicle", SCC$SCC.Level.Two, ignore.case=TRUE)
VehiclesSCC <- SCC[Vehicles,]$SCC
VehiclesNEI <- NEI[NEI$SCC %in% vehiclesSCC,]

BaltVehiclesNEI <- vehiclesNEI[vehiclesNEI$fips==24510,]

library(ggplot2)
ggp <- ggplot(BaltVehiclesNEI,aes(factor(year),Emissions)) +
  geom_bar(stat="identity",fill="grey",width=0.75) +
  theme_bw() +  guides(fill=FALSE) +
  labs(x="year", y=expression("Total PM"[2.5]*" Emission (10^5 Tons)")) + 
  labs(title=expression("PM"[2.5]*" Motor Vehicle Source Emissions in Baltimore (1999-2008)"))

print(ggp)

```

How have emissions from motor vehicle sources changed from 1999–2008 in Baltimore City?

Becausethe motors vehicles stop maked emissions from 1999-2008 in Baltimore City!

Question 6
Comparing emissions from motor vehicle sources in Baltimore City (fips == "24510") with emissions from motor vehicle sources in Los Angeles County, California (fips == "06037"),

```{r}
VehiclesBaltimoreNEI <- VehiclesNEI[VehiclesNEI$fips == 24510,]
VehiclesBaltimoreNEI$city <- "Baltimore City"
VehiclesLANEI <- VehiclesNEI[VehiclesNEI$fips=="06037",]
VehiclesLANEI$city <- "Los Angeles County"
bothNEI <- rbind(VehiclesBaltimoreNEI,VehiclesLANEI)


library(ggplot2)
 
ggp <- ggplot(bothNEI, aes(x=factor(year), y=Emissions, fill=city)) +
 geom_bar(aes(fill=year),stat="identity") +
 facet_grid(scales="free", space="free", .~city) +
 guides(fill=FALSE) + theme_bw() +
 labs(x="year", y=expression("Total PM"[2.5]*" Emission (Kilo-Tons)")) + 
 labs(title=expression("PM"[2.5]*" Motor Vehicle Source Emissions in Baltimore & LA, 1999-2008"))
 
print(ggp)
```

Which city has seen greater changes over time in motor vehicle emissions?

Los Angeles has seen the greatest changes over time in motor vehicle emissions from 1999 - 2008 but the best city on this kind is baltimore city.

